Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-04 doc/PRF2022/Supplementary.tex

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 0.5 that are initially confined in a square box.
The simulation results show the relaxation with the use of all three boundary conditions.
The color on the boundary from blue to red shows the magnitude of the boundary data and 
the range is from $\min g(\xx)$ to $\max g(\xx)$. All final configurations are adopted in 
simulations with hydrodynamic flows. The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
In this movie, there is no apparent structural rupture in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
In this movie, there is no apparent structural rupture in each case. For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the bilayer, 
$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
In this movie, some clear structural ruptures occur in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the bilayer, 
$\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.
In order to observe the structure behaviors at later time, we stabilize the frame by tracking the center of mass position of all JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
In this movie, some clear structural ruptures occur in each case. For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.\\

>>>>

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 1.25 nm that are initially confined in a square box.
The simulation results show the relaxation with the use of all three boundary conditions.
The color on the boundary from blue to red
is for $\min g(\xx)$ to $\max g(\xx)$.
All final configurations are adopted in 
simulations with hydrodynamic flows.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
The vesicle case undergoes tank treading
whereas the initially disordered BC (i) case
increases orientational order.  The multilamellar
assemply behaves a rigid body,
and the striated configuration moreso.
There are no ruptures that occur in this movie.\\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
at relatively low flow rates.
For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
disordered bilayer, 
$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
The vesicle stays inact, whereas the dissordered bilayer is pulled apart.
Like in Supplementary Movie S2, the striated assembly is basically rigid.\\

\noindent
{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow
at a higher shear rate. 
For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the
vesicle, $\dot\gamma = 0.1$ for the bilayer, 
$\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
The time step of all simulations is $\Delta t=0.2$.
In this movie, some clear structural ruptures occur in each case.
In order to observe the structure behaviors at later time,
we stabilize the frame by tracking the center of mass position of all JP. \\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
for high flow rates. 
In this movie, some clear structural ruptures occur in each case.
For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
In all cases, there is significant reduction in the orientational order of the assemblies.
While the BC (i) cases are broken into several pieces, the main body of the
BC (ii) and BC (iii) assemblies is not pulled apart by the background flow. 
\\
